A Technique for Inter-Retailer Recommendations

### 2014-06-12 paper2/paper.tex
Make minor tweaks/corrections.

\section*{Abstract}
\emph{The problem of making recommendation across retailers using only publicly
available information is explored. Experiments are conducted using real data in
which several recommender algorithms are compared. A novel latent feature
inter-retailer recommender algorithm that leverages public intra-retailer
recommendation information is described and shown to outperform a nontrivial
content-based approach.}

@@

The problem we examine here is, in many ways, more difficult than that of the
standard recommendation problem. Essentially, we would like to recommend an item
from retailer $X$ based solely on a known preference for an item from retailer
$Y$. For the product assortment problem, user purchase and rating information is
presumably known for one of the two retailers. In this study, however, we
simplify the scenario by making it symmetric. No user purchase or rating
information will be leveraged for either retailer. Instead, the algorithms
investigated here are limited to publicly available information, which includes
product descriptions and online product recommendations. Given the lack of
inter-retailer user data, a traditional CF technique is ostensibly not
applicable. Instead, we propose a new technique that leverages the recomender
graphs as well as the content from each product to create inter-retail
recommendations.

>>>>

\section*{Abstract}
\emph{The problem of making recommendations across retailers using only publicly
available information is explored. Experiments are conducted using real data in
which several recommender algorithms are compared. A novel latent feature
inter-retailer recommender system that leverages public intra-retailer
recommendation information is described and shown to outperform a nontrivial
content-based approach.}

@@

The problem we examine here is, in many ways, more difficult than that of the
standard recommendation problem. Essentially, we would like to recommend an item
from retailer $X$ based solely on a known preference for an item from retailer
$Y$. For the product assortment problem, user purchase and rating information is
presumably known for one of the two retailers. In this study, however, we
simplify the scenario by making it symmetric. No user purchase or rating
information will be leveraged for either retailer. Instead, the algorithms
investigated here are limited to publicly available information, which includes
product descriptions and online product recommendations. Given the lack of
inter-retailer user data, a traditional CF technique is ostensibly not
applicable. Instead, we propose a new technique that leverages the recommender
graphs as well as the content from each product to create inter-retailer
recommendations.
